### 2020-04-08 draft.tex
edits

Remarkably, all natural transformations between polynomial functors can be
represented in terms of their associated bundles. A natural transformation $P
\to P'$ corresponds to a pair of functions%
\footnote{We use dependent type syntax, e.g.\ as used in Idris.}
\[
\left( f : B \to B',\, f^{\sharp} : \dprod{b : B} E'_{fb} \to E_b \right)
\]
noting that $f$ acts covariantly on the base and $f^\sharp$ acts contravariantly on
fibers. 
In terms of bundles, a map $\pi\to\pi'$ is a diagram of the following sort:
\[
  \begin{tikzcd}
    E \arrow[d, "\pi"'] \arrow[r, leftarrow, "f_{\sharp}"] & \bullet \arrow[d] \arrow[r]
    \arrow[dr, phantom, "\ulcorner" very near start] & E' \arrow[d, "\pi'"] \\
    B \arrow[r, equals] & B \arrow[r, "f"'] & B'
  \end{tikzcd}
\]
We refer to these special spans as \emph{contravariant} morphisms of bundles.

@@

It turns out that these covariant maps of bundles correspond to natural
transformations between the appropriate sums of \emph{contravariant}
representables:
$$D(S) := \sum_{b \in B} E_b^S.$$

Polynomial functors as in \eqref{eqn.poly} get their name from the case in which
$B$ and $E$ are finite sets. Consider the function $\term{card}~E_{(-)} : B \to
\Nb$, which takes the cardinality of each fiber $E_b$. Letting $B_n :=
(\term{card}E_{(-)})\inv(n)$, i.e.\ $B_n$ is the set of elements whose fibers have $n$ elements,
we find that the for any set $X$, the cardinality
$$|P(X)| = \sum_{n \in \Nb} |B_n||X|^n$$
is a polynomial in the cardinality of $X$. Similarly,
$$|D(S)| = \sum_{n \in \Nb} |B_n|n^{|S|}$$
resembles a Dirichlet series in the cardinality of $S$ -- without the usual
negative sign.\footnote{Future work of the first author will recover the
  negative sign by generalizing the theory of Dirichlet functors to homotopy
  types.} Accordingly, we call such
sums of contravariant representables \emph{Dirichlet functors}.

@@

Analogously, we will prove the following theorem.
\begin{thm}
Let $D : \Set\op \to \Set$ be a contravariant functor. Then the following are
equivalent.
\begin{enumerate}
\item $D$ is Dirichlet.
\item $D$ is the sum of contravariant representables.
\item There is a bundle $\pi : E \to B$ together with a natural isomorphism
  $$D(X) \cong \sum_{b \in B} E_b^X.$$
  Or, equivalently, a natural isomorphism of $D$ with the composite
  $$\Set\op \xto{(\Delta_{!_B})\op} (\Set_{/B})\op \xto{[-, \pi]} \Set_{/B}
  \xto{\Sigma_{!_B}} \Set.$$
\item $D$ preserves connected limits.
\end{enumerate}
\end{thm}

Note that we no longer need to assume accessiblity. This is a general feature of
the theory of Dirichlet functors; it is a bit ``smaller'' and more manageable
than that of polynomials. In particular, a Dirichlet functor is determined by
its action on the terminal morphism $!_0 : 0 \to \ast$ of the empty set. As a corollary, Dirichlet functors form a topos.

\begin{thm}\label{thm:dirichlet.set.equivalence}
The functor $\Set^{\down} \to \type{Fun}(\Set\op, \Set)$, given by sending $\pi : E
\to B$ to the induced Dirichlet functor $X \mapsto \sum_{b \in B} E_b^X$, is
fully faithful, and so gives an equivalence
$$\Set^{\down} \simeq \Dir$$
between the topos of bundles and the category of Dirichlet functors, with inverse given by evalutation at
$!_0 : 0 \to \ast$.
\end{thm}

@@

\begin{acknowledgements}
Joyal, Kock(!), AFOSR. David Jaz Myers was supported by the National Science Foundation grant DMS-1652600 and Spivak was supported by AFOSR grants FA9550-19-1-0113 and FA9550-17-1-0058.
\end{acknowledgements}

@@

\begin{prop}\label{prop:adjoint.sextuple}
  There is an adjoint sextuple:
  \[
    \begin{tikzcd}
      \Set \arrow[r, "\const"] \arrow[r, leftarrow, shift left = 5,
      "\term{cod}"] \arrow[r, leftarrow, shift right = 5, "\term{dom}"]
      \arrow[r, shift left = 10, "!^{(-)}"]  \arrow[r, shift right = 10,
      "!_{(-)}"] \arrow[r, leftarrow, shift left = 15, "\term{ZC}"]& \Set^{\down}
    \end{tikzcd}
  \]
  All three functors $\Set \to \Set^{\down}$ are fully faithful.
\end{prop}
\begin{proof}
There is an adjoint triple $\begin{tikzcd} \ast \arrow[r,leftarrow] \arrow[r,
  bend left] \arrow[r, bend right] & \down \end{tikzcd}$. The middle three
functors---$\term{cod}$, $\const$, and $\term{dom}$---are given by restricting along this adjoint triple. The next two, $!_{(-)}$ and $!^{(-)}$, are
given by Kan extending, or more concretely:
  \begin{equation}\label{eqn.bangbang}
  X \mapsto \begin{tikzcd} 0 \arrow[d, "!^X"] \\ X \end{tikzcd}
  \qquad\text{and}\qquad
  X \mapsto \begin{tikzcd} X \arrow[d, "!_X"] \\ \ast \end{tikzcd}
  \end{equation}
 It is easy to see that the unit $X \to \term{dom} !_{X}$ is an isomorphism (it is in
fact an identity), so $!_{(-)}$ is fully faithful. Therefore, all three functors
going from $\Set \to \Set^{\down}$ are fully faithful.

The existence of the final adjoint can be deduced from the fact that $!^{(-)}$ preserves all
limits. It sends a bundle $\pi : E \to B$ to the largest subset $\term{ZC}(B)$ of $B$ for
which the following square is a pullback
\[
  \begin{tikzcd}[column sep=large]
0 \arrow[r] \arrow[d] \arrow[dr, phantom,
"\ulcorner" very near start] & E \arrow[d, "\pi"] \\
\term{ZC}(\pi) \arrow[r, hookrightarrow]                                       & B
\end{tikzcd}
\qedhere
\]
\end{proof}
We prove a few quick facts we will use later.
\begin{lem}\label{lem:bang.preserves.connected.colimits}
  The functor $!_{(-)}\colon\Set\to\Set^{\down}$ from \eqref{eqn.bangbang} preserves connected colimits.
\end{lem}
\begin{proof}
  To see that $!_{(-)}$ preserves connected colimits, recall that colimits in $\Set^{\down}$ are calculated pointwise. It remains to show, then, that the map of bundles
  \[
    \begin{tikzcd}
    \colim S_i \arrow[r, equals] \arrow[d] & \colim S_i \arrow[d] \\
    \colim \ast \arrow[r] & \ast 
    \end{tikzcd}
  \]
  is an isomorphism in $\Set^{\down}$, for which it suffices to show that
  $\colim \ast$ is terminal. But the colimit of a diagram of terminal objects is the set
  of connected components of its indexing category. Since we assumed the
  indexing category was connected, this contains a single element.
\end{proof}

@@

Now we will define the \emph{extent} of a bundle $\pi$ to be the Dirichlet functor $\ext_\pi: \Set\to\Set$ that it
corresponds to. This sends a bundle
$\pi : E \to B$ to the functor
$$X \mapsto \sum_{b \in B} E_b^X.$$
We will, however, give a more abstract definition of the extent, and then
calculate a number of presentations of it.

\begin{defn}\label{def.extent}
  Consider the functor $!_0\op \circ \sigma : \down \to \Set\op$ picking out the
  unique morphism $1\to 0$ in $\Set\op$. Sending a functor $\Set\op\to\Set$ to
  its precomposition with $!_0\op \sigma$ gives an evaluation functor
  $$\Set^{\down} \xleftarrow{\ev_{!_0}} \Fun(\Set\op, \Set).$$
  This functor admits a right adjoint by right Kan extension along $!_0\op \circ
  \sigma : \downarrow \to \Set\op$; we define the
  \emph{Dirichlet extent} functor $\ext : \Set^{\down} \to \Fun(\Set\op,
  \Set)$ to be this right adjoint. It sends any bundle $\pi$ to
  $$\ext_{\pi} :\equiv \term{ran}_{!_0\op \circ \sigma} \pi.$$
\end{defn}

\begin{prop}\label{prop:set.characterizing.extent}
  Let $\pi : E \to B$ be a bundle. The following are equivalent:
  \begin{enumerate}
  \item The extent $\ext_{\pi} : \Set\op \to \Set$ of $\pi$ from \cref{def.extent}.
  \item The functor
    $$S \mapsto \sum_{b \in B} E_b^S,$$
    or equivalently the composite
  $$\Set\op \xto{(B^{\ast})\op} (\Set_{/B})\op \xto{[-, \pi]} \Set_{/B}
  \xto{B_{\ast}} \Set.$$
\item The pullback in $\Fun(\Set\op, \Set)$:  
\[
\begin{tikzcd}
	\ext_\pi \ar[r]\ar[d]\arrow[dr, phantom,
      "\ulcorner" very near start]&
	B\ar[d]\\
	\Set(-,E)\ar[r]&
	\Set(-,B)
\end{tikzcd}
\]
\item The restricted representable functor
  $\Set^{\down}(!_{(-)}, \pi)$.
\item The functor
  $$S \mapsto \lim(\Hom_{\Set}(!_0, S)\op \to \down\op \xto{\sigma\op} \down \xto{\pi} \Set)$$
  where $\Hom_{\Set}(!_0, S)$ is the slice category of $!_0 : \down \to
  \Set$ over $S$.
\item The functor
  $$S \mapsto \lim(( S^{\triangleleft} )\op \xto{( !^{\triangleleft} )\op}
  (\ast^{\triangleleft})\op \xto{\sigma\op} \down
  \xto{\pi} \Set)$$
  where $(-)^{\triangleleft}$ is the \emph{left cone} 2-functor, adjoining an initial object.
  \end{enumerate}
\end{prop}
\begin{proof}
We have presented these results in order of most understandable to most
computational; we will prove it a somewhat opposite order.

First, we note that 
$$S \mapsto \lim(\Hom_{\Set\op}(S, !_0\op \circ \sigma) \to \down \xto{\pi} \Set)$$
is the right Kan extension formula for $\ext_{\pi} \equiv
\term{ran}_{!_0} \pi$. Now,
$\Hom_{\Set\op}(S, !_0\op \circ \sigma) \simeq \Hom_{\Set}(!_0 \circ \sigma\op,
S)\op$ over $\down$. Furthermore, we have the following equivalence:
\[
% https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBpiBdUkANwEMAbAVxiRAB12AJCAWwH1gnLnQC+ACgCE-YgAJOAYywAnBfPbYA5rzqcIaUrIDKASj1oQo0uky58hFGQCMVWoxZthfQcLFSZhqbmltYgGNh4BERO5K70zKyIHOxQEADuhFY2EfbRpC7U8R5JnKkZwaKuMFCa8ESgAGbKfEhkIDgQSDEgDHQARjAMAAq2kQ4gyliaABY4IIXuicnYvCGNzauIbR1IAExZIE0tiLvUO4gAzAsJnhpTOmuHG11nnZeVokA
\begin{tikzcd}
{\Hom_{\Set}(!_0 \circ \sigma\op, S)\op} \arrow[d, "\sim"'] \arrow[r] & \down \arrow[d, "\sigma"] \\
{\Hom_{\Set}(!_0, S)\op} \arrow[r]                                    & \down\op                 
\end{tikzcd}
\]
and therefore we may equivalently calculate this limit as 
$$\lim(\Hom_{\Set}(!_0, S)\op \to \down\op \xto{\sigma\op} \down \xto{\pi} \Set).$$
This gives us the equivalence between (1) and (5).

Now, the comma category $\Hom_{\Set}(!_0, S)$ simply adjoins an initial object
to (the discrete category) $S$. Therefore, we find that (5) and (6) are equivalent.

Now, we note that every set $S$ is the colimit of the diagram $S^{\triangleleft}
\xto{\ast^{\triangleleft}}\down \xto{!_0} \Set$, namely:
\[
% https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBoBGAXVJADcBDAGwFcYkRyQBfU9TXfIRTkK1Ok1btOPPtjwEiAZlE0GLNog7deIDHMFEALCvHqp22QIUoATCbWTNAHScBjKBBwIZu-vKHIdjZiDhogxBa++taBpMQhEmEAGtxiMFAA5vBEoABmAE4QALZIAKw0OBBIxD4FxWUVVYjktYUliOUglUg2rfUdjUiKfe1kXU0AbCNIIuNIUzp17XZziAt5bUODa1yUXEA
\begin{tikzcd}
              &              & S                                               &              &               \\
1 \arrow[rru] & 1 \arrow[ru] & \cdots                                          & 1 \arrow[lu] & 1 \arrow[llu] \\
              &              & 0 \arrow[llu] \arrow[lu] \arrow[ru] \arrow[rru] &              &              
\end{tikzcd}
\]
Since, by Lemma \ref{lem:bang.preserves.connected.colimits}, $!_{(-)}$
preserves connected colimits, we may make the following identification of (4)
with (6) using Lemma \ref{lem:set.bundle.yoneda}: 
\begin{align*}
  \Set^{\down}(!_S, \pi) &= \Set^{\down}(!_{\colim(S^{\triangleleft} \xto{!^{\triangleleft}} \ast^{\triangleleft} \xto{!_0} \Set)}, \pi) \\
  &\simeq \Set^{\down}(\colim(S^{\triangleleft} \xto{!^{\triangleleft}} \ast^{\triangleleft} \xto{!_0} \Set \xto{!_{(-)}} \Set^{\down}), \pi)\\
&\simeq \lim((S^{\down})\op \xto{(!^{\triangleleft})\op} (\ast^{\triangleleft})\op \xto{!_0\op} \Set\op \xto{!_{(-)}} (\Set^{\down})\op \xto{\Set^{\down}(-, \pi)} \Set) \\
&\simeq \lim((S^{\down})\op \xto{(!^{\triangleleft})\op} (\ast^{\triangleleft})\op \xto{\sigma\op} \down \xto{\pi} \Set).
\end{align*}

@@

Finally, we note that the set $\Set^{\down}(!_S, \pi)$ is naturally
isomorphic to the set $\sum_{b \in B} E_b^S$, letting us identify (4) with (2).
\end{proof}

@@

  As a corollary, the category of Dirichlet functors is a topos.
\end{thm}
\begin{proof}
Since $!_0 : \down \to \Set\op$ is fully faithful, the counit of the
$\ev_{!_0} \vdash \ext$ adjunction --- which is the universal cell defining the
right Kan extension --- is an isomorphism.

Now, we show that a functor is Dirichlet if and only if it is the extent of a bundle. If $D$ is
the extent of a bundle, then by Prop \ref{prop:set.characterizing.extent}, $D$ is naturally
isomorphic to the restricted representable $\Set^{\down}(!_{(-)})$. By Lemma
\ref{lem:bang.preserves.connected.colimits}, this sends connected colimits in $\Set$ to
connected limits.

Now, we show that if $D$ is Dirichlet, then the unit
$D \to \ext_{D!_0}$ is an isomorphism. By Prop
\ref{prop:set.characterizing.extent}, 
  $$\ext_{D!_0}(S) = \lim(S^{\triangleleft} \xto{!^{\triangleleft}} \ast^{\triangleleft}
  \xto{D!_0} \Set).$$

Every set $S$ is the connected colimit of the diagram $S^{\triangleleft} \to
\down \xto{!_0} \Set$, and therefore if $D$ preserves this limit, then
$D(S)$ is precisely the above limit $\ext_{D!_0}(S)$.
\end{proof}

\begin{rmk}
The six adjoints of Proposition \ref{prop:adjoint.sextuple} correspond, under
the equivalence of Theorem \ref{thm:dirichlet.set.characterization}, to
\begin{align*}
  \term{ZC}(D) &\sim \mbox{the coefficient of $0^S$ in $D$.}\\
  !^{C} &\sim S \mapsto C \times 0^S \\
  \cod(D) &\sim D(0) \\
  \const(C) &\sim S \mapsto C \\
  \dom(D) &\sim D(1) \\
  !_{C} &\sim S \mapsto C^S 
\end{align*}
In particular, $!_{(-)}$ corresponds to the Yoneda embedding.
\end{rmk}

\section{Cartesian Transformations between Dirichlet Functors}
In this section, we turn to cartesian transformations between Dirichlet
functors. We will show that the category of Dirichlet functors and cartesian
transfromations are equivalent to the category of Polynomial functors and
cartesian transformations.

\begin{prop}
A natural transformation $\phi : D \to D'$ between Dirichlet functors is
cartesian if and only if the induced bundle map $D!_0 \to D'!_0$ is a pullback.

>>>>

Remarkably, all natural transformations between polynomial functors can be
represented in terms of their associated bundles. A natural transformation $P
\to P'$ corresponds to a dependent pair of functions
\[
\left( f : B \to B',\, f^{\sharp} : \dprod{b : B} E'_{fb} \to E_b \right)
\]
noting that $f$ acts covariantly on the base and $f^\sharp$ acts contravariantly on
fibers. 
In terms of bundles, a map $\pi\to\pi'$ is a diagram of the following sort:
\[
  \begin{tikzcd}
    E \arrow[d, "\pi"'] \arrow[r, leftarrow, "f_{\sharp}"] & \bullet \arrow[d] \arrow[r]
    \arrow[dr, phantom, "\ulcorner" very near start] & E' \arrow[d, "\pi'"] \\
    B \arrow[r, equals] & B \arrow[r, "f"'] & B'
  \end{tikzcd}
\]
We refer to these special spans as \emph{contravariant} morphisms of bundles.

@@

It turns out that these covariant maps of bundles correspond to natural
transformations between the appropriate sums of \emph{contravariant}
representables:
$$D(X) := \sum_{b \in B} E_b^X.$$

Polynomial functors as in \eqref{eqn.poly} get their name from the case in which
$B$ and $E$ are finite sets. Consider the function $\term{card}~E_{(-)} : B \to
\Nb$, which takes the cardinality of each fiber $E_b$. Letting $B_n :=
(\term{card}E_{(-)})\inv(n)$, i.e.\ $B_n$ is the set of elements whose fibers have $n$ elements,
we find that the for any set $X$, the cardinality
$$|P(X)| = \sum_{n \in \Nb} |B_n||X|^n$$
is a polynomial in the cardinality of $X$. Similarly,
$$|D(X)| = \sum_{n \in \Nb} |B_n|n^{|X|}$$
resembles a Dirichlet series in the cardinality of $X$ -- without the usual
negative sign.\footnote{Future work of the first author will recover the
  negative sign by generalizing the theory of Dirichlet functors to homotopy
  types.} Accordingly, we call such
sums of contravariant representables \emph{Dirichlet functors}.

@@

Analogously, we will prove the following theorem.
\begin{thm}
Let $D : \Set\op \to \Set$ be a contravariant functor. Then the following are
equivalent.
\begin{enumerate}
\item $D$ is Dirichlet.
\item $D$ is the sum of contravariant representables.
\item There is a bundle $\pi : E \to B$ together with a natural isomorphism
  $$D(X) \cong \sum_{b \in B} E_b^X.$$
  Or, equivalently, a natural isomorphism of $D$ with the composite
  $$\Set\op \xto{(\Delta_{!_B})\op} (\Set_{/B})\op \xto{\Set_{/B}(-, \pi)} \Set_{/B}
  \xto{\Sigma_{!_B}} \Set.$$
\item $D$ preserves connected limits.
\end{enumerate}
\end{thm}

Note that we no longer need to assume accessiblity. This is a general feature of
the theory of Dirichlet functors; it is a bit ``smaller'' and more manageable
than that of polynomials. In particular, a Dirichlet functor is determined by
its action on the terminal morphism $!_0 : 0 \to 1$ of the empty set. As a corollary, Dirichlet functors form a topos.

\begin{thm}\label{thm:dirichlet.set.equivalence}
The functor $\Set^{\down} \to \type{Fun}(\Set\op, \Set)$, given by sending $\pi : E
\to B$ to the induced Dirichlet functor $X \mapsto \sum_{b \in B} E_b^X$, is
fully faithful, and so gives an equivalence
$$\Set^{\down} \simeq \Dir$$
between the topos of bundles and the category of Dirichlet functors, with inverse given by evalutation at
$!_0 : 0 \to 1$.
\end{thm}

@@

\begin{acknowledgements}
We appreciate helpful comments from Andr\'e Joyal and Joachim Kock on an early draft of this paper. Myers was supported by the National Science Foundation grant DMS-1652600, and Spivak was supported by AFOSR grants FA9550-19-1-0113 and FA9550-17-1-0058.
\end{acknowledgements}

@@

\begin{prop}\label{prop:adjoint.sextuple}
  There is an adjoint sextuple:
  \[
    \begin{tikzcd}
      \Set \arrow[r, "\const"] \arrow[r, leftarrow, shift left = 5,
      "\term{cod}"] \arrow[r, leftarrow, shift right = 5, "\term{dom}"]
      \arrow[r, shift left = 10, "!^{(-)}"]  \arrow[r, shift right = 10,
      "!_{(-)}"] \arrow[r, leftarrow, shift left = 15, "\term{ZC}"]& \Set^{\down}
    \end{tikzcd}
  \]
  All three functors $\Set \to \Set^{\down}$ are fully faithful.
\end{prop}
\begin{proof}
There is an adjoint triple $\begin{tikzcd} 1 \arrow[r,leftarrow] \arrow[r,
  bend left] \arrow[r, bend right] & \down \end{tikzcd}$. The middle three
functors---$\term{cod}$, $\const$, and $\term{dom}$---are given by restricting along this adjoint triple. The next two, $!_{(-)}$ and $!^{(-)}$, are
given by Kan extending, or more concretely:
  \begin{equation}\label{eqn.bangbang}
  X \mapsto \begin{tikzcd} 0 \arrow[d, "!^X"] \\ X \end{tikzcd}
  \qquad\text{and}\qquad
  X \mapsto \begin{tikzcd} X \arrow[d, "!_X"] \\ 1 \end{tikzcd}
  \end{equation}
 It is easy to see that the unit $X \to \term{dom} !_{X}$ is an isomorphism (it is in
fact an identity), so $!_{(-)}$ is fully faithful. Therefore, all three functors
going from $\Set \to \Set^{\down}$ are fully faithful.

The existence of the final adjoint can be deduced from the fact that $!^{(-)}$ preserves all
limits. It sends a bundle $\pi : E \to B$ to the largest subset $\term{ZC}(B)$ of $B$ for
which the following square is a pullback
\[
  \begin{tikzcd}[column sep=large]
0 \arrow[r] \arrow[d] \arrow[dr, phantom,
"\ulcorner" very near start] & E \arrow[d, "\pi"] \\
\term{ZC}(\pi) \arrow[r, hookrightarrow]                                       & B
\end{tikzcd}
\qedhere
\]
\end{proof}
We prove a few quick facts we will use later.
\begin{lem}\label{lem:bang.preserves.connected.colimits}
  The functor $!_{(-)}\colon\Set\to\Set^{\down}$ from \eqref{eqn.bangbang} preserves connected colimits.
\end{lem}
\begin{proof}
  To see that $!_{(-)}$ preserves connected colimits, recall that colimits in $\Set^{\down}$ are calculated pointwise. It remains to show, then, that the map of bundles
  \[
    \begin{tikzcd}
    \colim X_i \arrow[r, equals] \arrow[d] & \colim X_i \arrow[d] \\
    \colim 1 \arrow[r] & 1 
    \end{tikzcd}
  \]
  is an isomorphism in $\Set^{\down}$, for which it suffices to show that
  $\colim 1$ is terminal. But the colimit of a diagram of terminal objects is the set
  of connected components of its indexing category. Since we assumed the
  indexing category was connected, this contains a single element.
\end{proof}

@@

Now we will define the \emph{extent} of a bundle $\pi$ to be the Dirichlet functor $\ext_\pi: \Set\op\to\Set$ that it
corresponds to. This sends a bundle
$\pi : E \to B$ to the functor
$$\ext_\pi(X)\coloneqq \sum_{b \in B} E_b^X.$$
We will, however, give a more abstract definition of the extent, and then
calculate a number of presentations of it.

\begin{defn}\label{def.extent}
  Consider the functor $!_0\op \circ \sigma : \down \to \Set\op$ picking out the
  unique morphism $1\to 0$ in $\Set\op$. Sending a functor $\Set\op\to\Set$ to
  its precomposition with $!_0\op \circ\sigma$ gives an evaluation functor
  $$\Fun(\Set\op, \Set)\xto{\ev_{!_0}} \Set^{\down}.$$
  This functor admits a right adjoint by right Kan extension along $!_0\op \circ
  \sigma : \down \to \Set\op$; we define the
  \emph{Dirichlet extent} functor $\ext : \Set^{\down} \to \Fun(\Set\op,
  \Set)$ to be this right adjoint. It sends any bundle $\pi$ to
  $$\ext_{\pi} :\equiv \term{ran}_{!_0\op \circ \sigma} \pi.$$
\end{defn}

\begin{prop}\label{prop:set.characterizing.extent}
  Let $\pi : E \to B$ be a bundle. The following are equivalent:
  \begin{enumerate}
  \item The extent $\ext_{\pi} : \Set\op \to \Set$ of $\pi$ from \cref{def.extent}.
  \item The functor
    $$X \mapsto \sum_{b \in B} E_b^X,$$
    or equivalently the composite
  $$\Set\op \xto{(\Delta_B)\op} (\Set_{/B})\op \xto{\Set_{/B}(-, \pi)} \Set_{/B}
  \xto{\Sigma_B} \Set.$$
\item The pullback in $\Fun(\Set\op, \Set)$:  
\[
\begin{tikzcd}
	\ext_\pi \ar[r]\ar[d]\arrow[dr, phantom,
      "\ulcorner" very near start]&
	B\ar[d]\\
	\Set(-,E)\ar[r]&
	\Set(-,B)
\end{tikzcd}
\]
\item The restricted representable functor
  $\Set^{\down}(!_{(-)}, \pi)$.
\item The functor
  $$X \mapsto \lim(\Hom_{\Set}(!_0, X)\op \to \down\op \xto{\sigma\op} \down \xto{\pi} \Set)$$
  where $\Hom_{\Set}(!_0, X)$ is the comma category of $!_0 : \down \to
  \Set$ over $X:\ast\to\Set$.
\item The functor
  $$X \mapsto \lim(( X^{\triangleleft} )\op \xto{( !^{\triangleleft} )\op}
  (1^{\triangleleft})\op \xto{\sigma\op} \down
  \xto{\pi} \Set)$$
  where $(-)^{\triangleleft}$ is the \emph{left cone} 2-functor, adjoining an initial object.
  \end{enumerate}
\end{prop}
\begin{proof}
We have presented these results in order of most understandable to most
computational; we will prove it a somewhat opposite order.

First, we note that the conical limit formula for $\ext_{\pi} \equiv
\term{ran}_{!_0} \pi$ as a right Kan extension says
$$\ext_\pi(X)= \lim(\Hom_{\Set\op}(X, !_0\op \circ \sigma) \to \down \xto{\pi} \Set).$$
Now,
$\Hom_{\Set\op}(X, !_0\op \circ \sigma) \simeq \Hom_{\Set}(!_0 \circ \sigma\op,
X)\op$ over $\down$. Furthermore, we have the following equivalence:
\[
% https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBpiBdUkANwEMAbAVxiRAB12AJCAWwH1gnLnQC+ACgCE-YgAJOAYywAnBfPbYA5rzqcIaUrIDKASj1oQo0uky58hFGQCMVWoxZthfQcLFSZhqbmltYgGNh4BERO5K70zKyIHOxQEADuhFY2EfbRpC7U8R5JnKkZwaKuMFCa8ESgAGbKfEhkIDgQSDEgDHQARjAMAAq2kQ4gyliaABY4IIXuicnYvCGNzauIbR1IAExZIE0tiLvUO4gAzAsJnhpTOmuHG11nnZeVokA
\begin{tikzcd}
{\Hom_{\Set}(!_0 \circ \sigma\op, X)\op} \arrow[d, "\sim"'] \arrow[r] & \down \arrow[d, "\sigma"] \\
{\Hom_{\Set}(!_0, X)\op} \arrow[r]                                    & \down\op                 
\end{tikzcd}
\]
and therefore we may equivalently calculate this limit as 
$$\lim(\Hom_{\Set}(!_0, X)\op \to \down\op \xto{\sigma\op} \down \xto{\pi} \Set).$$
This gives us the equivalence between (1) and (5).

The comma category $\Hom_{\Set}(!_0, X)$ simply adjoins an initial object
to (the discrete category) $X$. Therefore, we find that (5) and (6) are equivalent.

Every set $X$ is the colimit of the diagram $X^{\triangleleft}
\xto{1^{\triangleleft}}\down \xto{!_0} \Set$, namely:
\[
% https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBoBGAXVJADcBDAGwFcYkRyQBfU9TXfIRTkK1Ok1btOPPtjwEiAZlE0GLNog7deIDHMFEALCvHqp22QIUoATCbWTNAHScBjKBBwIZu-vKHIdjZiDhogxBa++taBpMQhEmEAGtxiMFAA5vBEoABmAE4QALZIAKw0OBBIxD4FxWUVVYjktYUliOUglUg2rfUdjUiKfe1kXU0AbCNIIuNIUzp17XZziAt5bUODa1yUXEA
\begin{tikzcd}
              &              & X                                               &              &               \\
1 \arrow[rru] & 1 \arrow[ru] & \cdots                                          & 1 \arrow[lu] & 1 \arrow[llu] \\
              &              & 0 \arrow[llu] \arrow[lu] \arrow[ru] \arrow[rru] &              &              
\end{tikzcd}
\]
Since, by Lemma \ref{lem:bang.preserves.connected.colimits}, $!_{(-)}$
preserves connected colimits, we may make the following identification of (4)
with (6) using Lemma \ref{lem:set.bundle.yoneda}: 
\begin{align*}
  \Set^{\down}(!_X, \pi) &= \Set^{\down}(!_{\colim(X^{\triangleleft} \xto{!^{\triangleleft}} 1^{\triangleleft} \xto{!_0} \Set)}, \pi) \\
  &\simeq \Set^{\down}(\colim(X^{\triangleleft} \xto{!^{\triangleleft}} 1^{\triangleleft} \xto{!_0} \Set \xto{!_{(-)}} \Set^{\down}), \pi)\\
&\simeq \lim((X^{\triangleleft})\op \xto{(!^{\triangleleft})\op} (1^{\triangleleft})\op \xto{!_0\op} \Set\op \xto{!_{(-)}\op} (\Set^{\down})\op \xto{\Set^{\down}(-, \pi)} \Set) \\
&\simeq \lim((X^{\triangleleft})\op \xto{(!^{\triangleleft})\op} (1^{\triangleleft})\op \xto{\sigma\op} \down \xto{\pi} \Set).
\end{align*}

@@

Finally, we note that the set $\Set^{\down}(!_X, \pi)$ is naturally
isomorphic to the set $\sum_{b \in B} E_b^X$, letting us identify (4) with (2).
\end{proof}

@@

  As a corollary, the category of Dirichlet functors is a topos.
\end{thm}
\begin{proof}
Since $!_0 : \down \to \Set\op$ is fully faithful, the counit of the
$\ev_{!_0} \vdash \ext$ adjunction, the universal cell defining the
right Kan extension $\ext_-$, is an isomorphism. Thus $\ext$ is fully faithful. In what follows we show that a functor is Dirichlet---preserves connected limits---if and only if it is the extent of a bundle, proving the equivalence of $\Dir$ with $\Set^{\down}$.

If $D$ is
the extent of a bundle $\pi$, then by Prop \ref{prop:set.characterizing.extent}, $D$ is naturally
isomorphic to the restricted representable $\Set^{\down}(!_{(-)},\pi)$. By Lemma
\ref{lem:bang.preserves.connected.colimits}, this sends connected colimits in $\Set$ to
connected limits.

Now, we show that if $D$ is Dirichlet, then the unit
$D \to \ext_{D!_0}$ is an isomorphism. By Prop
\ref{prop:set.characterizing.extent}, 
  $$\ext_{D!_0}(X) = \lim(X^{\triangleleft} \xto{!^{\triangleleft}} 1^{\triangleleft}
  \xto{D!_0} \Set).$$
  Every set $X$ is the connected colimit of the diagram $X^{\triangleleft} \to
\down \xto{!_0} \Set$, and therefore if $D$ preserves this limit, then
$D(X)$ is precisely the above limit $\ext_{D!_0}(X)$.
\end{proof}

\begin{rmk}
The six adjoints of \cref{prop:adjoint.sextuple} correspond, under
the equivalence of \cref{thm:dirichlet.set.characterization}, to
\begin{align*}
  \term{ZC}(D) &\sim \mbox{the coefficient of $0^X$ in $D$.}\\
  !^{C} &\sim X \mapsto C \times 0^X \\
  \cod(D) &\sim D(0) \\
  \const(C) &\sim X \mapsto C \\
  \dom(D) &\sim D(1) \\
  !_{C} &\sim X \mapsto C^X 
\end{align*}
\dis{If we're using \cref{thm:dirichlet.set.characterization}, shouldn't we be thinking in terms of bundles?} In particular, $!_{(-)}$ corresponds to the Yoneda embedding.
\end{rmk}

\section{Cartesian Transformations between Dirichlet Functors}
In this section, we turn to cartesian transformations between Dirichlet
functors. We will show that the category of Dirichlet functors and cartesian
transfromations is equivalent to the category of polynomial functors and
cartesian transformations.

\begin{prop}\label{prop:set.dirichlet.cartesian.iff.bundle.cartesian}
A natural transformation $\phi : D \to D'$ between Dirichlet functors is
cartesian if and only if the induced bundle map $D!_0 \to D'!_0$ is a pullback.

As a corollary, the equivalence $\Dir \simeq \Set^{\down}$ restricts to an
equivalence
$$\Dir_{\ulcorner} \simeq \Set^{\down}_{\ulcorner}$$
between Dirichlet functors with cartesian natural transformations and bundles with
pullback squares.
\end{prop}
\begin{proof}
We want to show that for any $f\colon D\to D'$, the square
\begin{equation}\label{eqn.cart1}
\begin{tikzcd}
	D(1)\ar[r, "f_1"]\ar[d, "\pi"']&
	D'(1)\ar[d, "\pi'"]\\
	D(0)\ar[r, "f_0"']&
	D'(0)
\end{tikzcd}
\end{equation}
is a pullback in $\Set$ iff for all functions $g\colon X\to X'$, the naturality square
\begin{equation}\label{eqn.cart2}
\begin{tikzcd}
  D(X')\ar[r, "f_{X'}"]\ar[d, "D(g)"']&
  D'(X')\ar[d, "D'(g)"]\\
  D(X)\ar[r, "f_X"']&
  D'(X)
\end{tikzcd}
\end{equation}
is a pullback in $\Set$. We will freely use the natural isomorphism
$D(X)\cong\Set^{\down}(!_X, D!_0)$ from
\cref{prop:set.characterizing.extent}, which allows us to identify Diagram
\eqref{eqn.cart2} with
\begin{equation}\label{eqn.cart3}
\begin{tikzcd}
 \Set^{\down}(!_{X'}, D!_0)     \ar[r, "f_{!_0,1}"]\ar[d, "!_g^{1}"']& \Set^{\down}(!_{X'}, D'!_0)
  \ar[d, "!_{g}^{1}"]\\
  \Set^{\down}(!_{X}, D!_0)\ar[r, "f_{!_0, 1}"']&
 \Set^{\down}(!_X, D'!_0) 
\end{tikzcd}
\end{equation}

The square in Diagram \eqref{eqn.cart1} is a
special case of that in Diagram \eqref{eqn.cart2}, namely for $g\coloneqq !_0$;
this establishes the only-if direction.
